Convergent Evolution During Local Adaptation to Patchy Landscapes

### 2014-08-18 patchy-selection-paper.tex
thanked joachim

\subsection*{Acknowledgements}
We would like to acknowledge Michael Nachman, Steve Evans, and Yaniv Brandvain for useful discussions, 
as well as Gideon Bradburd, and Simon Aeschbacher and the rest of the Coop lab
for helpful comments and discussion of the manuscript.

>>>>

\subsection*{Acknowledgements}
We would like to heartily thank Joachim Hermisson for a careful reading of the paper,
and catching the algebra error present in the first version of this paper on the bioRxiv,
and also to acknowledge Michael Nachman, Steve Evans, and Yaniv Brandvain for useful discussions, 
as well as Gideon Bradburd, and Simon Aeschbacher and the rest of the Coop lab
for helpful comments and discussion of the manuscript.
